### 2014-09-18 ApTranscriptome_TR.Rmd
working pipeline to bootstrap gene expression quantification

# Load Bioconductor libraries
#source("http://bioconductor.org/biocLite.R")
#biocLite("topGO")
#biocLite("Rgraphviz")
#biocLite("GOSemSim")
library(topGO) 
library(Rgraphviz)	
library(GOSemSim)

@@

>>>>

# Load Bioconductor libraries
source("http://bioconductor.org/biocLite.R")
#biocLite("topGO")
#biocLite("Rgraphviz")
#biocLite("GOSemSim")
library(topGO) 
library(Rgraphviz)	
library(GOSemSim)

@@

samples <- c("A22-0", "A22-10", "A22-14", "A22-17", "A22-21", "A22-24", "A22-28", "A22-31", "A22-35", "A22-38", "A22-3", "A22-7", "Ar-0", "Ar-10", "Ar-14", "Ar-17", "Ar-21", "Ar-24", "Ar-28", "Ar-31", "Ar-35", "Ar-38", "Ar-3", "Ar-7")
